Dynamic Load Balancing for\\Heterogeneous Systems

### 2011-12-05 paper/paper.tex
Added new image for scheduling, and added experimental testbesd section.

\section{Load Balancing Benchmarks}

For this paper, three different benchmarks were used to assess the
effectiveness of the load balancer.  The first is a reduction benchmark,
in which the sum of variably-sized array is computed.  The reduction benchmark
is unique in that different code is being run on the CPU and the GPU.  The
reason for this is that the GPU cannot efficiently compute a reduction the way
a CPU typically would -- due to the relative inefficiency of backward branches
on the GPU.  A reduction on the GPU is a multi-stage process, in which the
output of one step is used as the input of the next.  Each steam processor
computes the reduction of two elements during each iteration, reducing the amount
of work during each step by a factor of two.  As a result, each step utilizes half
the stream processors of the previous step.  This continues until the reduction
operation is only done by a single stream processor.  A natural consequence of
this algorithm is that not all of the stream processors will be utilized during
the computation.

@@

\section{Load Balancing Schemes}
A naive implementation of CPU+GPU co-processing will in many cases lead to an imbalance
of work for either the CPU or GPU.  To deal with this problem we will investigate the
use of 2 different load balancing schemes in addition to the performance of a CPU-only or
a GPU-only solution.

@@

\section{Results and Analysis}
The three implemented benchmarks were run on a system with a discrete GPU, as well as
on a fused GPU platform.  In dynamic load balancing benchmarks, a chunk size of 80~KB
was used.  Dynamic results are only given for the discrete GPU testing environment,
as the APU platform was running Windows and our code was written with POSIX compliance
in mind.  In static load balancing benchmarks, the ratio of data computed on the GPU
will be specified.

>>>>

\section{Load Balancing Benchmarks}
For this paper, three different benchmarks were used to assess the
effectiveness of the load balancer.  The first is a reduction benchmark,
in which the sum of variably-sized array is computed.  The reduction benchmark
is unique in that different code is being run on the CPU and the GPU.  The
reason for this is that the GPU cannot efficiently compute a reduction the way
a CPU typically would -- due to the relative inefficiency of backward branches
on the GPU.  A reduction on the GPU is a multi-stage process, in which the
output of one step is used as the input of the next.  Each steam processor
computes the reduction of two elements during each iteration, reducing the amount
of work during each step by a factor of two.  As a result, each step utilizes half
the stream processors of the previous step.  This continues until the reduction
operation is only done by a single stream processor.  A natural consequence of
this algorithm is that not all of the stream processors will be utilized during
the computation.

@@

\section{Load Balancing Schemes}
A naive implementation of CPU+GPU co-processing will in many cases lead to an imbalance
of work for either the CPU or GPU.  To deal with this problem we will investigate the
use of 2 different load balancing schemes in addition to the performance of a CPU-only or
a GPU-only solution.  These schemes are illustrated in Figure~/ref{fig:scheduling}

@@

\begin{figure}[t]
\centering
\includegraphics[width=2.5in]{scheduling}
\caption{Data Partitioning Schemes for Load Balancing.}
\label{fig:scheduling}
\end{figure}

\section{Results and Analysis}
We tested the different benchmark applications using different hardware environments.
For the discrete GPU tests, we tested our application on an Intel Core Duo CPU with a
AMD HD5450 GPU attached via PCIe.  For the Fused CPU+GPU environment we used an AMD
Fusion A-3850.  Linux was used for the discrete environment, while Windows was used
on the Fused environment (in order to take advantage of newer drivers that allowed
for better hardware features on the new Fusion machine).

The three implemented benchmarks were run on a system with a discrete GPU, as well as
on a fused GPU platform.  In dynamic load balancing benchmarks, a chunk size of 80~KB
was used.  Dynamic results are only given for the discrete GPU testing environment,
as the APU platform was running Windows and our code was written with POSIX compliance
in mind.  In static load balancing benchmarks, the ratio of data computed on the GPU
will be specified.
